Improving Adaptive Seamless Designs through Bayesian optimization

### 2021-07-11 main.tex
appendix

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\linewidth]{generated/figures/plot_appendix_opt_epsilon.pdf}%
\includegraphics[width=0.5\linewidth]{generated/figures/plot_appendix_opt_thresh.pdf}
\caption{%
  This figure shows the location of the optimal values of $\varepsilon$ and $\tau$ for their respective rules obtained through the \emph{Grid} search, averaged across the 20 stochastic replications.
  It indicates that the search space for $r$ and $\varepsilon$ or $\tau$ is big enough but that each should be optimized on a $log$-scale.
  The color indicates the value of $y$, with \emph{red} beeing good.
  $y$-values are scaled for each single plot and cannot be compared across experiments.
  The best points are indicated through a white dot.
}
\label{fig:plot_opt_eps_thresh} 
\end{figure}

>>>>

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{generated/figures/plot_appendix_boxplot_paper_rev.pdf}
\caption{%
    Box plots that compares the performance (power) values on the effect set \emph{paper} and \emph{paper\_rev}.
    \emph{paper\_rev} is an additonal scenario, where the effects for the stage \emph{early} and \emph{final} are flipped.
  In contrast to \emph{paper}, the effect sizes are smaller for the \emph{early} stage.
}
\label{fig:plot_appendix_boxplot_paper_rev} 
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{generated/figures/plot_appendix_allbest_paper_rev.pdf}
\caption{%
  All evaluated configurations and their outcomes on the \emph{Grid} compared for the effect set \emph{paper} and \emph{paper\_rev}.
  For the epsilon and threshold rule only the curve for the $\epsilon$ and $\tau$ value with highest power ($y$) is displayed.
}
\label{fig:plot_appendix_allbest_paper_rev} 
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\linewidth]{generated/figures/plot_appendix_opt_epsilon.pdf}%
\includegraphics[width=0.5\linewidth]{generated/figures/plot_appendix_opt_thresh.pdf}
\caption{%
  This figure shows the location of the optimal values of $\varepsilon$ and $\tau$ for their respective rules obtained through the \emph{Grid} search, averaged across the 20 stochastic replications.
  It indicates that the search space for $r$ and $\varepsilon$ or $\tau$ is big enough but that each should be optimized on a $log$-scale.
  The color indicates the value of $y$, with \emph{red} beeing good.
  $y$-values are scaled for each single plot and cannot be compared across experiments.
  The best points are indicated through a white dot.
}
\label{fig:plot_appendix_opt_episolon_thresh} 
\end{figure}
